Static contract checking for Haskell

### 2011-10-19 paper.tex
paper update + cosmetic fix
Added a Latex annotations package (trackchanges.sty) and some examples.
I'll now erase the examples and get to work annotating the paper.  The
trackchanges is from http://trackchanges.sourceforge.net/ and includes a
Python based gui that I did not try or include here.

@@

Our approach to static contract-checking is to translate source code
to a first-order logic theory and then use an automated theorem prover
to check the consistency of the theory.

Consider:
\begin{verbatim}
data List a = Nil | Cons a (List a)

@@

Now that we translated everything to first-order logic, we can ask the
theorem prover if the theory formed by those formulae is
consistent, ie if $T \vdash \phi$.

@@

\begin{figure*}
  $$ \ruleform{\ctrans{contract} = \Phi} $$
\begin{eqnarray*}
  \ctrans{e \in \{x \mid b(x) \}} &=&  \min{\etrans{b(e)}} \land (\etrans{b(e)} = true \lor \etrans{e} = \unr)\\
  \ctrans{e \in x:c_1 \to c_2(x)} &=& \forall x.~\min{\etrans{e(x)}} \to (\ctrans{x \not \in c_1} \lor  \ctrans{\etrans{e(x)} \in c_2(x)})\\
  \ctrans{e \in \cfc} &=& \cf{\etrans{e}}
\end{eqnarray*}

\begin{eqnarray*}
  \ctrans{e \not \in \{x \mid b(x) \}} &=&  \min{\etrans{b(e)}} \land (\etrans{b(e)} = false \lor \etrans{e} = \bad)\\
  \ctrans{e \not \in x:c_1 \to c_2(x)} &=& \exists x.~ \ctrans{x \in c_1} \land  \ctrans{\etrans{e(x)} \not \in c_2(x)}\\
  \ctrans{e \not \in \cfc} &=& \lnot \cf{\etrans{e}}
\end{eqnarray*}

>>>>

% Margin notes (ugly and complicated)
%% \usepackage[draft]{fixme}
%% \fxusetheme{color}
%% %\fxusetheme{signature}
%% %\fxuselayouts{pdfmargin}
%% %\fxusetargetlayout{color}
%% \FXRegisterAuthor{nc}{anc}{NC}

% Margin notes round two (easier and better looking)
%
% http://trackchanges.sourceforge.net/help_stylefile.html
\usepackage[inline]{trackchanges} % [margins] is also good
\addeditor{nc}

@@

Our approach to static contract-checking is to translate source code
to a first-order \note[nc]{this is a note} logic theory and
 then use an \annote[ncc]{this is an annote}{automated theorem prover}
\add[nc]{new text} to check the \remove[nc]{consistency} of the theory.
\change[nc]{Old text}{New text}.
Consider:
\begin{verbatim}
data List a = Nil | Cons a (List a)

@@

\ncnote*{Thi is  a note}{Now that we translated} everything to first-order logic, we can ask the
theorem prover if the theory formed by those formulae is
consistent, ie if $T \vdash \phi$.

@@

\begin{figure*}
  $$ \ruleform{\ctrans{contract} = \Phi} $$
\begin{eqnarray*}
  \ctrans{e \in \{x \mid b \}} &=&  \min{\etrans{b[e/x]}} \land (\etrans{b[e/x]} = true \lor \etrans{e} = \unr)\\
  \ctrans{e \in x:c_1 \to c_2} &=& \forall x.~\min{\etrans{e~x}} \to (\ctrans{x \not \in c_1} \lor  \ctrans{e~x \in c_2})\\
  \ctrans{e \in \cfc} &=& \min{\etrans{e}} \land \cf{\etrans{e}}
\end{eqnarray*}

\begin{eqnarray*}
  \ctrans{e \not \in \{x \mid b \}} &=&  \min{\etrans{b[e/x]}} \land (\etrans{b[e/x]} = false \lor \etrans{e} = \bad)\\
  \ctrans{e \not \in x:c_1 \to c_2} &=& \exists x.~ \ctrans{x \in c_1} \land  \ctrans{e~x \not \in c_2}\\
  \ctrans{e \not \in \cfc} &=& \min{\etrans{e}} \land \lnot \cf{\etrans{e}}
\end{eqnarray*}
